---
title: "Randomness Study"
author: "Yanruyu Zhu (yaz4004)"
date: "11/16/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
```{r}
library(escalation)
library(BOIN)
```

```{r}
View(get_three_plus_three)
#View(simulate_trials)
```
function (selector_factory, num_sims, true_prob_tox, true_prob_eff = NULL, 
  ...) 
{
  sim_func <- simulation_function(selector_factory)
  if (is.null(true_prob_eff)) {
    l <- lapply(1:num_sims, function(x) sim_func(selector_factory, 
      true_prob_tox, ...))
  }
  else {
    l <- lapply(1:num_sims, function(x) sim_func(selector_factory, 
      true_prob_tox, true_prob_eff = true_prob_eff, ...))
  }
  simulations(fits = l, true_prob_tox = true_prob_tox, true_prob_eff = true_prob_eff, 
    ...)
    
```{r}
View(simulation_function)
```
function (selector_factory) 
{
  UseMethod("simulation_function")
}

```{r}
methods(simulation_function)
#getAnywhere(simulation_function.derived_dose_selector_factory)
```
```{r}
View(get.oc)
```


